\documentclass[]{deedy-resume-openfont}
\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\namesection{}{Balachander Padmanabha}{ 
\href{mailto:bala.8644@gmail.com}{bala.8644@gmail.com \enspace} \textbullet{} \enspace 858-729-3622 \enspace \textbullet{} \enspace La Jolla, CA 
}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{UC San Diego}
\descript{M.S in Computer Science}
\location{Expected December, 2017}
\sectionsep

\subsection{R.V.C.E}
\descript{B.E in Information Science}
\location{Grad. June, 2013 | Bangalore, India}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Github:// \href{https://github.com/bala8}{\custombold{bala8}} \\
LinkedIn://  \href{https://www.linkedin.com/in/balacp/}{\custombold{balacp}} \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{SKILLS}

\subsection{Languages}
C/C++ \textbullet{} Java \textbullet{} Python \textbullet{} C\#\\ 
Docker \textbullet{} SQL \textbullet{} Hadoop \textbullet{} PySpark \\
HTML \textbullet{} CSS \textbullet{} JavaScript \textbullet{} PHP \\
\sectionsep

\subsection{Tools}
Linux \textbullet{} Git \textbullet{} Jupyter \textbullet{} GDB  \\
Valgrind \textbullet{} IntelliJ \textbullet{} Eclipse\\
Agile/Scrum \textbullet{} Perforce
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\subsection{Graduate}
\textbullet{} Distributed Systems \\
\textbullet{} Computer Security \\
\textbullet{} Data Mining \& Analytics  \\
\textbullet{} Computer Communication Networks\\
\textbullet{} Operating Systems \\
\textbullet{} Recommender Systems \& Web Mining \\
\textbullet{} Artificial Intelligence  \\
\textbullet{} Algorithm Design \& Analysis \\
\textbullet{} Principles of Database Systems \\
\textbullet{} Principles of Programming Languages \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Awards} 
\textbullet{} Winner - DCCSG India Hackathon for "Self Defined Adaptive Management System" application. \\
\textbullet{} 1st Prize - Samsung Mobile Innovator Program for "Travel Buddy" Android application. \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     roles
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Leadership Roles} 
\textbullet{} VP - The Entrepreneur Challenge (2017)\\
\textbullet{} Lead - ECN India, Cisco (2014-2016)\\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Objective
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Objective}
\location{Seeking Full-Time Software Engineering Position starting early 2018.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Professional Experience}
\runsubsection{Aruba Networks}
\descript{| Software Engineering Intern }
\location{June 2017 – September 2017 | Santa Clara, CA | C++, Python}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Designed \& developed dynamic end-to-end telemetry monitor for available bandwidth utilization \& adaptive QoS infra for SD-WAN Mobility Controller, enabling competitive market advantage for the product. 
\item Helped reduce overall policy enforcement module defect backlog by 65\% in first 2 months. 
\end{tightemize}
\sectionsep

\runsubsection{UC San Diego}
\descript{| Graduate Teaching Assistant }
\location{March 2017 - December 2017 | San Diego, CA}
\begin{tightemize} 
\item Course: CSE 123 (Computer Networks) 
\item Involved conducting quizzes, lab/discussion sessions \& evaluating projects for 300+ undergraduate students. 
\end{tightemize}
\sectionsep

\runsubsection{Cisco Systems}
\descript{| Software Engineer II }
\location{August 2013 – August 2016 | Bangalore, India | C/C++, Python, Docker, GDB}
\begin{tightemize}
\item Worked on Data Center Switching product line.
\item Gained expertise \& took up complete ownership for Auto-configuration, DHCP \& packet manager modules.
\item Also contributed to feature development \& customer escalations for Programmable fabric, VxLAN \& K-stack.
\item Helped mentor 5-6 senior engineers \& new hires in Auto-configuration and DHCP modules. 
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     projects
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{PROJECTS}

\runsubsection{Distributed File System}
\location{Java, Docker}
\begin{tightemize}
\item Developed a distributed fault tolerant file system upon which users can perform create, delete \& query operations. It includes self-initiated replication, file locking \& load-balancing via threshold metrics ensuring consistency \& integrity. It was built using a custom Java RMI implementation.
\end{tightemize}
\sectionsep

\runsubsection{Facebook: Check-Ins Prediction}
\location{Python, Jupyter}
\begin{tightemize}
\item Built a Recommender System using Facebook's anonymized check-in dataset from Kaggle (roughly 30 million data-points). Performed exploratory analysis \& implemented an Ensemble of generative models (K-NN, Logistic Regression, Naive Bayes) to predict future user check-Ins achieving 65\% accuracy.
\end{tightemize}
\sectionsep

\runsubsection{Lightweight DHCPv6 Relay Agent}
\location{C/C++, Python}
\begin{tightemize}
\item Implementation of RFC 6221 for Cisco Nexus 5600 platform. Involved in system design, development of the feature, unit/integration testing and automation scripting. 
\end{tightemize}
\sectionsep

\runsubsection{Smart-Crop}
\location{Java, Hadoop, Ganglia, SQL}
\begin{tightemize}
\item Implemented SVM \& Random Forest algorithm for Hyper-spectral satellite image classification in a distributed environment. It managed to get result for land cover classification \& crop stage analysis with an accuracy of 74\%. 
\end{tightemize}
\sectionsep

\end{minipage} 
\end{document}  \documentclass[]{article}